Reproducible Research - Project 1
=======================
##Instructions  
1.Code for reading in the dataset and/or processing the data  
2.Histogram of the total number of steps taken each day  
3.Mean and median number of steps taken each day  
4.Time series plot of the average number of steps taken  
5.The 5-minute interval that, on average, contains the maximum number of steps  
6.Code to describe and show a strategy for imputing missing data  
7.Histogram of the total number of steps taken each day after missing values are imputed   
8.Panel plot comparing the average number of steps taken per 5-minute interval across weekdays and weekends  
9.All of the R code needed to reproduce the results (numbers, plots, etc.) in the report  


**1.Code for reading in the dataset and/or processing the data**

```{r}
unzip("activity.zip",exdir = "data")
```
Reading the data into activity data frame and show some summary statistics

```{r}
activity <- read.csv("data/activity.csv", stringsAsFactors=FALSE)
str(activity)
```

Summary of the Data file

```{r}
summary(activity)

```

**2.Histogram of the total number of steps taken each day**

```{r}
stepsPerDay <- aggregate(steps ~ date, activity, sum, na.rm=TRUE)  ## First get the total steps per day

### Now plot the Histogram

hist(stepsPerDay$steps)
```

**3.Mean and median number of steps taken each day **  
### Use mean and median functions on the stepsperday data

```{r}
meansteps <- mean(stepsPerDay$steps)
mediansteps <- median(stepsPerDay$steps)
meansteps
mediansteps
```
**4.Time series plot of the average number of steps taken**  

```{r}
stepsPerInterval<-aggregate(steps~interval, data=activity, mean, na.rm=TRUE)
plot(steps~interval, data=stepsPerInterval, type="l")
```

**5.The 5-minute interval that, on average, contains the maximum number of steps  **   

Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?

```{r}
stepsPerInterval[which.max(stepsPerInterval$steps),]$interval
```

**6.Code to describe and show a strategy for imputing missing data **  
 
```{r}
totalNA <- sum(is.na(activity$steps))
totalNA
```

The stragegy employed will the missing values in the dataset with the mean per interval. the below r code will return, for a particular interval, the mean value

```{r}
getMeanStepsPerInterval<-function(interval){
    stepsPerInterval[stepsPerInterval$interval==interval,]$steps
}
```  

Create a new dataset that is equal to the original dataset but with the missing data filled in with the mean from above.

```{r}
activityNoNA<-activity
for(i in 1:nrow(activityNoNA)){
    if(is.na(activityNoNA[i,]$steps)){
        activityNoNA[i,]$steps <- getMeanStepsPerInterval(activityNoNA[i,]$interval)
    }
}
```

The new data set with no missing values is contained in the variable activityNoNA

**7.Histogram of the total number of steps taken each day after missing values are imputed **  

```{r}
totalStepsPerDayNoNA <- aggregate(steps ~ date, data=activityNoNA, sum)
hist(totalStepsPerDayNoNA$steps)
```

    
